Automated discovery \\ of interpretable gravitational-wave population models

### 2022-07-11 src/tex/ms.tex
Split title cleaner
Fix some typos

\twocolumn[
\icmltitle{Automated discovery of interpretable gravitational-wave population models}

@@

While most ML algorithms optimizie a fixed set number of real parameters,
Symbolic regression is a machine learning (ML) algorithm for regression which searches for analytic expressions which optimize some loss function.
The search typically employs a ``genetic algorithm'', which arranges symbols in a tree, evaluates the resultant expression, and repeats this process until a particular goal is met.
Since models for physical phenomena are often specified in a language of concise mathematical expressions, symbolic regression can produce interpretable models compared to traditional ML, as the ``trained model'' generated by symbolic regression is in the same \textit{language} as existing physical models (i.e., analytic expressions).
Therefore, symbolic regression can produce insights for science in a way that traditional ML cannot.

>>>>

\twocolumn[
\icmltitle{
Automated discovery \\
of interpretable gravitational-wave population models}

@@

While most ML algorithms optimize a fixed set number of real parameters,
Symbolic regression is a machine learning (ML) algorithm which searches for analytic expressions which optimize some loss function.
The search typically employs a ``genetic algorithm'', which arranges symbols in a tree, evaluates the resultant expression, and repeats this process until a particular goal is met.
Since models for physical phenomena are often specified in a language of concise mathematical expressions, symbolic regression can produce interpretable models compared to traditional ML, as the ``trained model'' generated by symbolic regression is in the same \textit{language} as existing physical models (i.e., analytic expressions).
Therefore, symbolic regression can produce insights for science in a way that traditional ML cannot.
